A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-12 tex/main.tex
Make minor adjustment to abstract.

\abstract{The Iterated Prisoner's Dilemma is a well established framework for
          the study of emergent behaviour. In this paper an extensive numerical
          study of the evolutionary dynamics of this framework are presented.

@@

I'm happy to write this section. We can lift some references from one of my
papers on the Moran process.

>>>>

\begin{abstract}
    The Iterated Prisoner's Dilemma is a well established framework for
          the study of emergent behaviour. In this paper an extensive numerical
          study of the evolutionary dynamics of this framework are presented.

@@

Some work has looked at evolutionary stability of strategies within the
Prisoner's Dilemma \cite{Li2014} but this is not done in the more widely used
setting of the Moran process but in terms of infinite population stability.

In \cite{Baek2016} Moran processes are looked at in a theoretic framework for a
small subset of strategies.

In \cite{Lee2015} machine learning techniques are used to train a strategy
capable of resisting invasion and also invade any memory one strategy.
